General constraints on magic distillation protocols from statistical mechanics

### 2021-05-11 magic_paper.tex
Added plots on F, phi variation

The above bound demonstrates how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
The analysis involved makes simplifying assumptions that could easily be dropped, at the price of more complex expressions. For example, we can obtain general expressions without any assumptions on $\epsilon, \epsilon'$ or without performing any Clifford change in basis.
We could also perform similar analysis for general qudits, and different choices of magic states. It might also be of interest to consider other choices of reference states that may include more appropriate hardware physics, for example for photonic set-ups.

@@

\begin{figure}[t!]
    \centering
    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
    \caption{\textbf{Temperature-dependent bounds for magic distillation.}
  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state. The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$. The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star(\beta)$ for $\beta \leq \beta_\star$. \nick{Refer to definitions of starred quantities} The $\beta = 0$ line corresponds to the regime in which the magic protocol corresponds to a unital channel.
    }
    \label{fig:rate_contour}
\end{figure}

@@

@@

\ddd{[Need some numerics on varying the $F'$ case]}

\section{Outlook and open questions}
\label{sec:lower_bounds}

@@

\subsection{Dropping pre/post-processing of the magic states}
If we drop the freedom to transform them magic states via Clifford unitaries that depend on the reference states $\tau$ and $\tau'$, then the analysis just presented gets a little more complex, since the largest component in the rescaled distribution depends on a number of factors. We illustrate this by the following result.

>>>>

\iffalse
\begin{figure}[t!]
    \centering
    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
    \caption{\textbf{Temperature-dependent bounds for magic distillation.}
  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state. The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$. The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star(\beta)$ for $\beta \leq \beta_\star$. \nick{Refer to definitions of starred quantities} The $\beta = 0$ line corresponds to the regime in which the magic protocol corresponds to a unital channel.
    }
    \label{fig:rate_contour}
\end{figure}
\fi

\begin{figure}[t!]
    \centering
    \subfigure[][]{%
    \label{fig:noCliff}%
    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}}\\
    \subfigure[][]{%
    \label{fig:Cliff}%
    \includegraphics[scale=0.4]{figs/rate_scatter_cliff.pdf}}
    \caption{\textbf{Temperature-dependent bounds for magic distillation.} \nick{Need to replot with one shared colorbar} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state. The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$. The $\beta = 0$ line corresponds to the regime in which the magic protocol corresponds to a unital channel.
\subref{fig:noCliff} No additional Clifford processing is performed to obtain this plot. The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star(\beta)$ for $\beta \leq \beta_\star$, as defined in~\cref{app:cliff_processing}.
 \subref{fig:Cliff} Clifford processing was performed resulting in a smooth bound.}
    \label{fig:rate_contour}
\end{figure}

\cref{thm:free-energy} is a demonstration of how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
The analysis involved makes simplifying assumptions that could easily be dropped, at the price of more complex expressions. For example, we can obtain general expressions without any assumptions on $\epsilon, \epsilon'$ or without performing any Clifford change in basis.
We could also perform similar analysis for general qudits, and different choices of magic states. It might also be of interest to consider other choices of reference states that may include more appropriate hardware physics, for example for photonic set-ups.

@@

@@

\subsection{\nick{Numerics on varying $F, \phi$}}

@@

\nick{Below are some interesting findings}

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{figs/test/R_vs_E1.pdf}
    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,E,10)$ and $H' = \rm{diag}(0,E',10)$.
    }
    \label{fig:rvse1}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{figs/test/R_vs_E2.pdf}
    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,5,E)$ and $H' = \rm{diag}(0,5,E')$.
    }
    \label{fig:rvse2}
\end{figure}

\begin{figure}[t!]
    \centering
    \subfigure[][]{%
    \label{fig:phip}%
    \includegraphics[scale=0.4]{figs/test/phi_p.pdf}}\\
    \subfigure[][]{%
    \label{fig:Rp}%
    \includegraphics[scale=0.4]{figs/test/rate_p.pdf}}
    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = p\ {\rm{diag}}(0,1,2) + (1-p)\ {\rm{Hadamard}}$.
\subref{fig:noCliff} Plot of $\phi$ vs $p$
 \subref{fig:Cliff} Plot of $R$ vs $p$}
    \label{fig:vsp}
\end{figure}

Performing the standard 3D-rotation matrix 
\begin{equation}
\begin{pmatrix}
\sin{\theta}\cos{\varphi} & \sin{\theta}\sin{\varphi} & \cos{\theta}\\
\cos{\theta}\cos{\varphi} & \cos{\theta}\sin{\varphi} & -\sin{\theta}\\
-\sin{\varphi} & \cos{\varphi} & 0
\end{pmatrix}
\end{equation}
on $H$ to get $H'$ leaves $\phi$ unaffected.

\null\newpage
\null\newpage
\section{Outlook and open questions}
\label{sec:lower_bounds}

@@

\subsection{Dropping pre/post-processing of the magic states}
\label{app:cliff_processing}

If we drop the freedom to transform them magic states via Clifford unitaries that depend on the reference states $\tau$ and $\tau'$, then the analysis just presented gets a little more complex, since the largest component in the rescaled distribution depends on a number of factors. We illustrate this by the following result.
